### 2019-05-18 Plan/pages/work_plan.tex
Changes; - Updated the main README.md for the project - Added some more papers
Changes; - Added archive folder - Added metaphone similar technique to C++ project - Small project re-structuring

\section{Literature review}
\label{litReview}
\textbf{Duration}: ? 
\\\\
This stage will involve reviewing the research into producing near collisions with SHA1. This may also extend into producing a review around full collisions of SHA1.
\par
SHA1 has been selected due to its vulnerability. Methods for producing collisions have been known for a long time and it seems the algorithm is on its way out of mainstream use.

\section{Formulation specific research questions}
\textbf{Duration}: ?
\\\\
Questions may currently involve:

\begin{itemize}
    \item What is the probability of producing near-collisions with SHA1?
    \item What would be the complexity in storage and computation?
    \item Can such near-collisions be generated e.g. using the university’s high-performance computing facilities? 
\end{itemize}

Further questions may be added using information gained from already performed research.

\section{Implementing near-collision code}
\label{code}
\textbf{Duration}: ?
\\\\
This section will involve the actual implementation of code using knowledge gained through the literature review. This may be pre-existing code manipulated to work on the university’s HPC cluster.

\section{Determining metrics for measuring experiments}

Ways to measure the progress of a project

\section{Experimentation stage}

\textbf{Duration}: ?
\\\\
This stage will involve running experiments to gain complexity data. This may involve working on further research and validating results.

\section{Thesis/Paper writing}

\textbf{Duration}: ?
\\\\
This will involve the creation of a \textasciitilde70 page dissertation alongside a condensed paper for submission to a journal

>>>>

\section{Project title/goal}

{
    \small
    "Investigating the feasibility of generating near-collisions for pEp TrustWords and its affect on security"

    \textbf{Points: } \\
    Use-case for TrustWords:
    \begin{itemize}
        \item Users are often deterred by difficulty in key authentication (e.g. PGP web-of-trust).
    \end{itemize}
}

\subsection{RFC drafts}
{
\small
\verb|draft-marques-pep-handshake-02|
\\
\textit{"Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.  Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."}

Showing that 4 words is too low in certain cases could be very useful?

\verb|draft-birk-pep-trustwords-00|
\\
In another draft document it also states:

\textit{"It is for further study, what minimal number of words (or entropy) should be required."}

This shows there is some sort of research gap.
}

\section{Literature review}
\label{litReview}

{
\small
\textbf{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}\\
Paper shows the usability of current schemes. The can be useful to show the need for trustwords and how they would fit in. Maybe even that the security needs improving for word based auth schemes?

\textbf{Can Unicorns Help Users Compare Crypto Key Fingerprints?}\\
Another paper talking about the usability of user authentication schemes.

\textbf{An Empirical Study of Textual Key-Fingerprint Representations}\\
Another study on the usability of methods of comparing key-fingerprints. This one highlights on the high usability of words.

}

\section{Formulation specific research questions}
What is the purpose of this project and how could it be useful?

\newpage
\section{Methods for creating similarities in words}

Visual: 
\begin{itemize}
    \item Levenshtein 
\end{itemize}

Auditory:
\begin{itemize}
    \item Soundex
    \item Metaphone (successor to Soundex)
\end{itemize}

Combined:
\begin{itemize}
    \item Metaphone + Levenshtein
\end{itemize}

\section{Experimentation}
What do we want to look at?
